Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-01-01 output/paper/_figures.qmd
Added YML file for paper-specific authors and added some authors. Modyfing tables so that match style of AJE. Added abbreviations EDCs and steroids in text paper. Extending labels tabels.

## Marginal comparisons

@@

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Marginal comparison results for $hitrtse \sim edc$
#| fig-width: 9
#| fig-height: 10

@@

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Marginal comparison results for $production \sim edc$
#| fig-width: 9
#| fig-height: 12

@@

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Marginal comparison results for $hitrtse \sim metabolite$
#| fig-width: 9
#| fig-height: 5

>>>>

## Marginal contrasts

@@

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Marginal contrast results for $hitrtse \sim edc$
#| fig-width: 9
#| fig-height: 10

@@

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Marginal contrast results for $production \sim edc$
#| fig-width: 9
#| fig-height: 12

@@

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Marginal contrast results for $hitrtse \sim metabolite$
#| fig-width: 9
#| fig-height: 5

### 2024-01-01 output/paper/_si.qmd
Added YML file for paper-specific authors and added some authors. Modyfing tables so that match style of AJE. Added abbreviations EDCs and steroids in text paper. Extending labels tabels.

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    lloq = "loq"
  )
gt::gt(lloq_mets |> dplyr::arrange(metabolite)) |>
  gt::tab_footnote(
    footnote = "Lower limit of quantification expressed in nanograms per millilitre.",
    locations = gt::cells_column_labels(
      columns = lloq
    )
  )
```
Lower limits of quantification for the corticosteroids
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var,
                              st = 1, en = 3) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest(append_to_chem = NULL)$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
Classification of the measured corticosteroids, by cohort.
:::

@@

### Marginal comparisons for effect modification

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $hitrtse \sim edc \times sex$
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $metabolite \sim edc \times sex$
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $hitrtse \sim metabolite \times sex$
:::

>>>>

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    lloq = "loq"
  )
gt::gt(lloq_mets |> dplyr::arrange(metabolite)) |>
  gt::tab_footnote(
    footnote = "Lower limit of quantification expressed in nanograms per millilitre.",
    locations = gt::cells_column_labels(
      columns = lloq
    )
  )
```
Lower limits of quantification for the glucocorticosteroids
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var,
                              st = 1, en = 3) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest(append_to_chem = NULL)$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
Classification of the measured glucocorticosteroids, by cohort.
:::

@@

### Marginal contrasts for effect modification

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal contrast results for $hitrtse \sim edc \times sex$
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal contrast results for $metabolite \sim edc \times sex$
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal contrast results for $hitrtse \sim metabolite \times sex$
:::

### 2024-01-01 output/paper/_tables.qmd
Added YML file for paper-specific authors and added some authors. Modyfing tables so that match style of AJE. Added abbreviations EDCs and steroids in text paper. Extending labels tabels.

```{r pop-desc}
#| label: tbl-pop-desc
#| tbl-cap: Characteristics of the children included in the analyses, by cohort and overall

@@

```{r edc-desc}
#| label: tbl-edc-desc
#| tbl-cap: Levels of unprocessed chemicals, by cohort and overall

@@

## Corticosteroids

```{r met-desc}
#| label: tbl-met-desc
#| tbl-cap: Levels of unprocessed corticosteroids, by cohort and overall

@@

```{r hypothesis-1}
#| label: tbl-hypothesis-1
#| tbl-cap: Hypothesis testing results of effect modification by sex for $hitrtse \sim edc$

@@

```{r hypothesis-2}
#| label: tbl-hypothesis-2
#| tbl-cap: Hypothesis testing results of effect modification by sex for $metabolite \sim edc$

@@

```{r hypothesis-3}
#| label: tbl-hypothesis-3
#| tbl-cap: Hypothesis testing results of effect modification by sex for $hitrtse \sim metabolite$

>>>>

```{r pop-desc}
#| label: tbl-pop-desc
#| tbl-cap: Participant characteristics, by cohort and overall (HELIX Study; 2013-2016).

@@

```{r edc-desc}
#| label: tbl-edc-desc
#| tbl-cap: Participants endocrine disruptors concentrations, by cohort and overall (HELIX Study; 2013-2016).

@@

## Glucocorticosteroids

```{r met-desc}
#| label: tbl-met-desc
#| tbl-cap: Participants glucocorticosteroids concentrations, by cohort and overall (HELIX Study; 2013-2016).

@@

```{r hypothesis-1}
#| label: tbl-hypothesis-1
#| tbl-cap: Hypothesis testing results of effect modification by sex for $hitrtse \sim edc$.

@@

```{r hypothesis-2}
#| label: tbl-hypothesis-2
#| tbl-cap: Hypothesis testing results of effect modification by sex for $metabolite \sim edc$.

@@

```{r hypothesis-3}
#| label: tbl-hypothesis-3
#| tbl-cap: Hypothesis testing results of effect modification by sex for $hitrtse \sim metabolite$.
